---
title: "p8105_hw2_ncl2127"
author: "Nisha Lingam"
date: "2023-10-01"
output: github_document
---
##need to be aware of arguments into a function that predates tidyverse

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(readxl)
```
## Problem 1

```{r}

```


## Problem 2
```{r mr_trash_wheel creation, filtered irrelevant rows, updated homes_powered column}
mr_trash_wheel = read_excel("./data/202309 Trash Wheel Collection Data.xlsx", sheet = 1, cell_rows(c(2:549)))|>
  janitor::clean_names() |>
  mutate(homes_powered = (weight_tons*500)/30) |>
  mutate(wheel_type = "mr") |>
  select(-c(x15, x16))

mr_trash_wheel$year = as.numeric(mr_trash_wheel$year)
```

```{r prof_trash_wheel creation, filtered irrelevant rows, updated homes_powered column}
prof_trash_wheel = read_excel("./data/202309 Trash Wheel Collection Data.xlsx", sheet = 2, cell_rows(c(2:108)))|>
  janitor::clean_names() |>
  mutate(homes_powered = (weight_tons*500)/30) |>
  mutate(wheel_type = "prof")
```

```{r gwynnda_trash_wheel creation, filtered irrelevant rows, updated homes_powered column}
gwynnda_trash_wheel = read_excel("./data/202309 Trash Wheel Collection Data.xlsx", sheet = 4, cell_rows(c(2:157)))|>
  janitor::clean_names() |>
  mutate(homes_powered = (weight_tons*500)/30) |>
  mutate(wheel_type = "gwynnda")
```

```{r}
data_wheels = 
  full_join(mr_trash_wheel, prof_trash_wheel) |>
  full_join(x = _, gwynnda_trash_wheel)

view(data_wheels)

```
The `pols` data has `r nrow(pols)` observations and `r ncol(pols)` variables and tells us about the party affiliation distribution (democrat or republican) for governors and senators for a given year from years `r range(pols$year)[1]` to `r range(pols$year)[2]`. It also tells us whether the sitting president was a democrat or republican. The `snp` data has `r nrow(snp)` observations and `r ncol(snp)` variables, ranging from years `r range(snp$year)[1]` to `r range(snp$year)[2]`. The `unemployment` data has `r nrow(unemployment)` observations and `r ncol(unemployment)` variables ranging from years `r range(unemployment$year)[1]` to `r range(unemployment$year)[2]`. In Januarys in or after 1975 in which a democrat was president, the **average unemployment rate was `r filter(data_538, month == "January", year >= 1975, president == "dem") |> pull(unemployment) |> mean() |> round(2)`**.  The average unemployment rate over the same time period in which a republican was president was `r filter(data_538, month == "January", year >= 1975, president == "gop") |> pull(unemployment) |> mean() |> round(2)`.


## Problem 3
```{r clean and tidy mci_baseline}
mci_baseline = read_csv("./data/data_mci/data_mci/MCI_baseline.csv")|>
  janitor::clean_names() |>
  filter(!is.na(Age_at_onset))

```