---
title: "p8105_hw2_ncl2127"
author: "Nisha Lingam"
date: "2023-10-01"
output: github_document
---
##need to be aware of arguments into a function that predates tidyverse

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(readxl)
```
## Problem 1

```{r}

```

## Problem 2
```{r mr_trash_wheel creation, filtered irrelevant rows, updated homes_powered column}
mr_trash_wheel = read_excel("./data/202309 Trash Wheel Collection Data.xlsx", sheet = 1, cell_rows(c(2:549)))|>
  janitor::clean_names() |>
  mutate(homes_powered = (weight_tons*500)/30) |>
  mutate(wheel_type = "mr") |>
  select(-c(x15, x16))

mr_trash_wheel$year = as.numeric(mr_trash_wheel$year)
```

```{r prof_trash_wheel creation, filtered irrelevant rows, updated homes_powered column}
prof_trash_wheel = read_excel("./data/202309 Trash Wheel Collection Data.xlsx", sheet = 2, cell_rows(c(2:108)))|>
  janitor::clean_names() |>
  mutate(homes_powered = (weight_tons*500)/30) |>
  mutate(wheel_type = "prof")
```

```{r gwynnda_trash_wheel creation, filtered irrelevant rows, updated homes_powered column}
gwynnda_trash_wheel = read_excel("./data/202309 Trash Wheel Collection Data.xlsx", sheet = 4, cell_rows(c(2:157)))|>
  janitor::clean_names() |>
  mutate(homes_powered = (weight_tons*500)/30) |>
  mutate(wheel_type = "gwynnda")
```

```{r}
data_wheels = 
  full_join(mr_trash_wheel, prof_trash_wheel) |>
  full_join(x = _, gwynnda_trash_wheel)

view(data_wheels)

```
The `mr_trash_wheel` data has `r nrow(mr_trash_wheel)` observations and `r ncol(mr_trash_wheel)` variables and tells us about the amount in tons and types of trash collected ranging from `r range(mr_trash_wheel$year)[1]` to `r range(mr_trash_wheel$year)[2]`. The `prof_trash_wheel` data has `r nrow(prof_trash_wheel)` observations and `r ncol(prof_trash_wheel)` variables, ranging from years `r range(prof_trash_wheel$year)[1]` to `r range(prof_trash_wheel$year)[2]`. The `gwynnda_trash_wheel` data has `r nrow(gwynnda_trash_wheel)` observations and `r ncol(gwynnda_trash_wheel)` variables ranging from years `r range(gwynnda_trash_wheel$year)[1]` to `r range(gwynnda_trash_wheel$year)[2]`.  The total weight of trash collected by Professor Trash Wheel was `r sum(prof_trash_wheel$weight_tons)`**.

## Problem 3
```{r clean and tidy mci_baseline}
mci_baseline = read_csv("./data/data_mci/data_mci/MCI_baseline.csv")|>
  janitor::clean_names() |>
  
  rename(age_of_onset = age_at_the_onset_of_mci_missing_if_a_subject_remains_mci_free_during_the_follow_up_period, sex = x1_male_0_female, apoe4_status = x1_apoe4_carrier_0_apoe4_non_carrier) |>
  
  filter(!row_number() %in% c(1), age_of_onset 
         != ".") |>
  mutate(
    sex = replace(sex, sex == 0, "female"),
    sex = replace(sex, sex == 1, "male"),
    apoe4_status = replace(apoe4_status, apoe4_status == 1, "carrier"),
    apoe4_status = replace(apoe4_status, apoe4_status == 0, "non-carrier")
  )

```